---
title: "Homework 6"
format: pdf
editor: visual
bibliography: hw_6_refs.bib
csl: https://www.zotero.org/styles/apa
execute: 
  echo: false
  eval: true
fig-width: 6.5
fig-height: 8
---

## Commit 1

```{r}
library(ggplot2)
library(tidyverse)
library(here)
library(readr)
library(kableExtra)
library(modelsummary)
library(dplyr)
library(tinytex)

star<-read_csv(here("data", "star.csv"))

```

## Commit 2

As suggested by @divecha2023, tables and figures were used to increase the readability of our document. We used R and packages called tidyverse and ggplot2 to create tables and figures [@R; @tidyverse; @ggplot2].

## Commit 3

```{r}

summary_table <- star %>%
  group_by(sex, frl) %>%
  summarise(
    math_mean = round(mean(tmathss, na.rm = TRUE), 2),
    math_sd   = round(sd(tmathss, na.rm = TRUE), 2),
    rdg_mean  = round(mean(treadss, na.rm = TRUE), 2),
    rdg_sd    = round(sd(treadss, na.rm = TRUE), 2)
  )

datasummary_df(summary_table, output = "kableExtra") 



```

Table interpretation

The table shows that both boys and girls who are not eligible for free/reduced lunch have higher average math and reading scores. Girls tend to slightly outperform boys in both subjects, while FRL students have lower average scores, highlighting socioeconomic disparities in achievement.

Commit 4

\\newpage

#References
